Binocular combination in the autonomic nervous system

### 2024-05-22 manuscript.Rmd
Testing processdata level 2
Processdata 2

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$
 | & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: pnas.csl
header-includes:
  \usepackage{caption}
  \usepackage{lineno} \linenumbers
---

@@

processdata <- 0 # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

>>>>

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
 | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: pnas.csl
header-includes:
  \usepackage{caption}
  \usepackage{lineno} \linenumbers
---

@@

processdata <- 2 # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)
